---
title: "Santander"
author: "Keith Hultman"
date: "March 13, 2016"
output: html_document
---

### From the Competition page:
Santander Bank is asking Kagglers to help them identify dissatisfied customers early in their relationship. Doing so would allow Santander to take proactive steps to improve a customer's happiness before it's too late.

You are provided with an anonymized dataset containing a large number of numeric variables. The "TARGET" column is the variable to predict. It equals one for unsatisfied customers and 0 for satisfied customers.

The task is to predict the probability that each customer in the test set is an unsatisfied customer.

```{r Load Data}
setwd("~/github/Santander")
train <- read.csv("train.csv", stringsAsFactors = TRUE)
test <- read.csv("test.csv")

```

```{r Explore dataset}
summary(train)
dim(train)
colnames(train)
head(train)

train$TARGET <- as.factor(train$TARGET)
```

```{r Principal Components Analysis}
# I'm not sure if I need to normalize the data first

# train.pca1 <- princomp(train, scores = TRUE)
# train.pca1 <- princomp(train, scores = TRUE, cor=TRUE)
# These resulted in errors, presumably due to data not being normalized

sum(is.na(train))
# There are no NAs in data

scaled.train <- scale(train)
summary(scaled.train)
train.pca1 <- princomp(scaled.train, scores = TRUE, cor = TRUE)
```

