---
title: "Santander"
author: "Keith Hultman"
date: "March 13, 2016"
output: html_document
---

### From the Competition page:
Santander Bank is asking Kagglers to help them identify dissatisfied customers early in their relationship. Doing so would allow Santander to take proactive steps to improve a customer's happiness before it's too late.

You are provided with an anonymized dataset containing a large number of numeric variables. The "TARGET" column is the variable to predict. It equals one for unsatisfied customers and 0 for satisfied customers.

The task is to predict the probability that each customer in the test set is an unsatisfied customer.

```{r Load Data}
setwd("~/github/kaggle-santander")
train <- read.csv("train.csv", stringsAsFactors = TRUE)
test <- read.csv("test.csv", stringsAsFactors = TRUE)

```

```{r Data Cleaning}
dim(train)
colnames(train)

sum(is.na(train))
# There are no NAs in data




str(train)

# Identify which columns need to be set to logical or factor
# Start with known logical column
# TARGET is 0 if satisfied, and 1 if unsatisfied
train$TARGET <- as.factor(train$TARGET)

# Search for columns with only 2 unique numbers
cols.to.factor <- sapply(train, function(col) (length(unique(col)) <= 2))

# Set those columns to Factor
train[ , cols.to.factor] <- lapply(train[ , cols.to.factor] , factor)
# This has the downside of setting columns other than 0/1 to factors 
# For example there are several 0 or 3 columns - I'm fine with this for now

str(train)

library(ggplot2)



```

```{r Principal Components Analysis}
# I'm not sure if I need to normalize the data first

# train.pca1 <- princomp(train, scores = TRUE)
# train.pca1 <- princomp(train, scores = TRUE, cor=TRUE)
# These resulted in errors, presumably due to data not being normalized

scaled.train <- train

# Normalize data set so that mean is 0 and standard deviation is 1
col.to.scale <- sapply(scaled.train, is.numeric)
scaled.train[col.to.scale] <- lapply(scaled.train[col.to.scale], scale)

str(scaled.train)


train.pca1 <- princomp(scaled.train, scores = TRUE, cor = TRUE)
```

